Analysis

### 2022-04-07 analysis/analysis.Rmd
prep submission

---
title: "PragBat Analysis"
output: html_document
---

@@

```{r}
wide_data <- data %>%
  mutate(task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inference (1)",
                    `simple_inf` = "Informativeness Inference (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Relational Match-to-sample"))%>%
  filter(study != "study3",
         task != "training") %>%
  droplevels() %>%
  group_by(study,id,task, test_day) %>%
  summarise(mean = mean(correct)) %>%
  spread(test_day, mean) %>%
  na.omit() %>%
  rename("Day1" = `1`,
         "Day2" = `2`)

@@

cor_r1 <- data %>%
  mutate(task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inference (1)",
                    `simple_inf` = "Informativeness Inference (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Relational Match-to-sample"))%>%
  filter(study == "study1") %>%
  droplevels() %>%
  group_by(id,task) %>%
  summarise(mean = mean(correct)) %>%
  spread(task, mean) %>%
  ungroup() %>%
  select(-id) %>%
  corrr::correlate(diagonal = reli %>%
                     filter(study == "study1") %>%
                     pull(reli)) %>%
  gather(task, cor, -term) %>%
  mutate(cor = replace(cor, duplicated(cor), NA)) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  na.omit() %>%
  mutate(study = "study1")%>%
  left_join(mcor)%>%
  mutate(cor2 = ifelse(!is.na(mcor), paste0(" ",cor,"\n"," [",round(mcor,2), "]"), cor))

cor_r2 <- data%>%
    mutate(task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inference (1)",
                    `simple_inf` = "Informativeness Inference (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Relational Match-to-sample"))%>%
  filter(study == "study2") %>%
  droplevels() %>%
  group_by(id,task) %>%
  summarise(mean = mean(correct)) %>%
  spread(task, mean) %>%
  ungroup() %>%
  select(-id) %>%
  corrr::correlate(diagonal = reli%>%filter(study == "study2") %>%pull(reli)) %>%
  gather(task, cor, -term) %>%
  mutate(cor = replace(cor, duplicated(cor), NA)) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  na.omit() %>%
  mutate(study = "study2")%>%
  left_join(mcor)%>%
  mutate(cor2 = ifelse(!is.na(mcor), paste0(" ",cor,"\n"," [",round(mcor,2), "]"), cor))

cor3 <- data%>%
    mutate(task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inference (1)",
                    `simple_inf` = "Informativeness Inference (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Relational Match-to-sample"))%>%
  filter(study == "study3")%>%
  filter(task != "training")%>%
  droplevels()%>%
  group_by(id,task)%>%
  summarise(mean = mean(correct))%>%
  spread(task, mean)%>%
  ungroup()%>%
  select(-id)%>%
  corrr::correlate(diagonal = c(1,1.1,1.2,1.3,1.4))%>%
  gather(task, cor, -term)%>%
  mutate(cor = replace(cor, duplicated(cor), NA))%>%
  mutate_if(is.numeric, round, digits = 2)%>%
  na.omit()%>%
  mutate(study = "study3",
         cor = ifelse(cor>0.99,NA,cor))

@@

ggsave(plot = pf4,"../paper/figures/figure4.png", width = 10, height = 3, scale = 1.5, bg = "white")
```

>>>>

---
title: "Analysis"
output: html_document
---

@@

```{r}
wide_data <- data %>%
  mutate(task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inf. (1)",
                    `simple_inf` = "Informativeness Inf. (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Rel. Match-to-sample"))%>%
  filter(study != "study3",
         task != "training") %>%
  droplevels() %>%
  group_by(study,id,task, test_day) %>%
  summarise(mean = mean(correct)) %>%
  spread(test_day, mean) %>%
  na.omit() %>%
  rename("Day1" = `1`,
         "Day2" = `2`)

@@

cor_r1 <- data %>%
  mutate(task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inf. (1)",
                    `simple_inf` = "Informativeness Inf. (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Rel. Match-to-sample"))%>%
  filter(study == "study1") %>%
  droplevels() %>%
  group_by(id,task) %>%
  summarise(mean = mean(correct)) %>%
  spread(task, mean) %>%
  ungroup() %>%
  select(-id) %>%
  corrr::correlate(diagonal = reli %>%
                     filter(study == "study1") %>%
                     pull(reli)) %>%
  gather(task, cor, -term) %>%
  mutate(cor = replace(cor, duplicated(cor), NA)) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  na.omit() %>%
  mutate(study = "study1")%>%
  left_join(mcor)%>%
  mutate(cor2 = ifelse(!is.na(mcor), paste0(" ",cor,"\n"," [",round(mcor,2), "]"), cor))

cor_r2 <- data%>%
    mutate(task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inf. (1)",
                    `simple_inf` = "Informativeness Inf. (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Rel. Match-to-sample"))%>%
  filter(study == "study2") %>%
  droplevels() %>%
  group_by(id,task) %>%
  summarise(mean = mean(correct)) %>%
  spread(task, mean) %>%
  ungroup() %>%
  select(-id) %>%
  corrr::correlate(diagonal = reli%>%filter(study == "study2") %>%pull(reli)) %>%
  gather(task, cor, -term) %>%
  mutate(cor = replace(cor, duplicated(cor), NA)) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  na.omit() %>%
  mutate(study = "study2")%>%
  left_join(mcor)%>%
  mutate(cor2 = ifelse(!is.na(mcor), paste0(" ",cor,"\n"," [",round(mcor,2), "]"), cor))

cor3 <- data%>%
    mutate(task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inf. (1)",
                    `simple_inf` = "Informativeness Inf. (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Rel. Match-to-sample"))%>%
  filter(study == "study3")%>%
  filter(task != "training")%>%
  droplevels()%>%
  group_by(id,task)%>%
  summarise(mean = mean(correct))%>%
  spread(task, mean)%>%
  ungroup()%>%
  select(-id)%>%
  corrr::correlate(diagonal = c(1,1.1,1.2,1.3,1.4))%>%
  gather(task, cor, -term)%>%
  mutate(cor = replace(cor, duplicated(cor), NA))%>%
  mutate_if(is.numeric, round, digits = 2)%>%
  na.omit()%>%
  mutate(study = "study3",
         cor = ifelse(cor>0.99,NA,cor))

@@

ggsave(plot = pf4,"../paper/figures/figure4.png", width = 10, height = 3, scale = 1.3, bg = "white")
```
